### 2022-11-15 NSF2022/Description/specificaim1v2.tex
SA1 minor changes
small change
SA3
spell checked SA1

\subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
\label{sec:specificaim1}
We introduced~\eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
existing methods for studing vesicles and bilayers. The simulation
results in Figures~\ref{fig:JPv_linearshear} and~\ref{fig:JPv_rupture}
show that two-dimensional, granule-based vesicles replicate the
equilibria and hydrodynamics for continuous curves~\cite{FuQuRyYo22,
Fu2018_SIAM}. Our next goal is to study the model using rigorous
analysis and consider three-dimensionsional effects.

@@

\begin{wrapfigure}[11]{r}{0.5\textwidth}
  \vspace{-8pt}
  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:amphiphilic_assembly} \footnotesize
  Self-organization under amphiphilic boundary condition. (a) Granules
  first match hydrophobic tails (red), (b) then align length-wise. (c)
  The same pattern of self-organization holds in three dimensions, as
  simulated by Kohl, Corona, and
  Veerapaneni~\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
In the double-well potential case, equation~\eqref{eqn:phase} is a
nonlinear Allen-Cahn equation. This situation models granules immersed
in a two-phase fluid (e.g., granules in an emulsion) where there is an
interesting interplay between the long-range alignment of granules and
the diffusive interface energy of the free boundary between fluid
phases. On unbounded domains like $\Omega(t)$, Allen-Cahn equations can
have multiple solutions~\cite{Alama1997StationaryLS,
Alikakos2008OnAE, Bronsard1993OnTB, Byeon2014SolutionsOH, Byeon2013OnAP,
Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF}.
To have one solution $\phi$ for each $t$, 
we must reformulate~\eqref{eqn:phase} as
the following initial value problem with transport:
\begin{align}
  \label{eqn:phase_transport}
  \phi_t + \uu \cdot \nabla
  = -\beta \frac{\delta E}{\delta \phi}
  = \beta(\epsilon^2 \Delta \phi - W'(\phi)),
  \quad \phi(\xx,0) = \phi_0(\xx),
\end{align}
for initial data $\phi_0$. The modified system enjoys an energy law
similar to~\eqref{eq:energy_law} with an addtional dissipation term
involving the square the Euler-Lagrange derivative $\frac{\delta
E}{\delta \phi}$ and dampening factor $\beta > 0$. There are several
works dealing with the characterization of the geometric evolution of
interfaces under the Allen-Cahn and Cahn-Hilliard
equations~\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF,
Dai2019WeakSF, Promislow2017ExistenceBA, Dai2015CompetitiveGE,
Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
Dai2013GeometricEO, Promislow2022UndulatedBI, Gera2017CahnHilliardOS}
and well-posedness
results when coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
Liu2012StrongSF, Giorgini2019WellPosednessOA, Wu2022WellposednessOA,
Gal2010AsymptoticBO, Giorgini2020DiffuseIM, Giorgini2019UniquenessAR}.
The proposed research extends these results to problems with moving
domains. A closely related and strongly developing direction in the area
of nematics liquid crystals concerns the interaction of Landau-de Gennes
functionals with colloids, and studies the qualitative structure of
defects around single or multiple coloidal
particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
  Alama2021SaturnRD, PhysRevE.96.042702}.

@@

The second problem considers the approximation of elastic energy of
curves and surfaces, and seeks to make rigorous the simulation results
of~\cite{FuQuRyYo22, Fu2018_SIAM}. We employ the so-called
``amphiphilic'' boundary condition that leads a collection of
granules to form bilayers. Referring to
Figure~\ref{fig:amphiphilic_assembly}, 
\begin{align}
\label{eq:amphiphilic_BC}
  \phi(\xx) = \tfrac{1}{2}\left(\dd_i \cdot 
    (\xx - \aa_i)/c_i + 1\right), \quad \xx \in \Gamma_i,
\end{align}
where $\dd_i$ is the director, $\|\dd_i\| = 1$,
$\aa_i$ is the center, and $c_i$ the
``radius'' of the $i$th granule. The phase $\phi$ takes values close to
$1$ in the direction $\dd_i$, representing a hydrophobic tail, and
values close to $0$ in the direction $\dd_i$ representing the
hydrophilic head.

@@

Sharp interface models represent a membrane vesicle as an
inextensible, continuous, closed surface $\Sigma$ with elastic energy
\begin{align}
  \label{eq:Canham-Helfrich}
  \int_{\Sigma} k_B(H - k_0)^2\, dS,
\end{align}
where $H$ is the mean curvature, $k_0$ is a spontaneous curvature, and
$k_B$ is a bending modulus. One can also account
for spatially dependent spontaneous curvature
\cite{PhysRevE.79.031926,Lowengrub13,mahapatra_saintillan_rangamani_2020}
and for extensibility by
including in~\eqref{eq:Canham-Helfrich} an additional stretching term
$k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are
the deformed and equilibrium area densitities respectively
\cite{chabanon2017}.

@@

Finally, to consider three-dimensionsional effects, we will generalize
Problem 2 to \emph{numerically} study the energies of amphiphilic
granules confined to surfaces. Recent works on nematics on a surface have
studied the interplay between surface geometry and a director
field~\cite{Nestler2020PropertiesOS, Nitschke2018NematicLC,
Nestler2018OrientationalOO, Nitschke2019HydrodynamicII,
Nitschke2020LiquidCO}. Researchers have formulated finite element
methods~\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
Nestler2019AFE} and studied minimizers~\cite{Segatti2014EquilibriumCO,
Segatti2014AnalysisOA}. In biophysics, researchers
have derived the generalized Helfrich energy for lipid bilayers that
involves coupling effects between lipid tilt to director
splay~\cite{Hamm2000ElasticEO, Terzi2019CurvatureTiltTO, Terzi2019ACQ,
  Terzi2017NovelTC, Pinigin2020NewCT,Rangamani20140463}. It contains~\eqref{eq:Canham-Helfrich}
as a special case.
\begin{quotation}
  \noindent
  \textbf{Problem 3.} Simulate surfaces made up of three-dimensional,
  amphilic granules. Numerically investigate the limiting energy for
  large-$N_b$ suspensions.
\end{quotation}
We will study Problem 3 by simulating large granule-number membranes.
If, after thoroughly sampling shapes and boundary conditions,
it turns out that the granule energies are not described by
a nematic or  Helfrich-type energy, then we will change
hypotheses and look for alternative sharp interface elastic energies.
PI Ryham is well-qualified to lead this investigation.
In his much noticed Biophysical Journal and Nature
papers~\cite{RyKlYaCo16, Chetal16}, he calculated least energy
paths for \emph{membrane fusion} using a surface-director model based on
the general Helfrich energy. The energy barriers 
proved consistent with later results from molecular dynamic
simulation and experiment~\cite{SmRiMu19, 2017PNAS..114.1238F}.

>>>>

\subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
\label{sec:specificaim1}
We introduced~\eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
existing methods for studying vesicles and bilayers. The simulation
results in Figures~\ref{fig:JPv_linearshear} and~\ref{fig:JPv_rupture}
show that two-dimensional, granule-based vesicles replicate the
equilibria and hydrodynamics for continuous curves~\cite{FuQuRyYo22,
Fu2018_SIAM}. Our next goal is to study the model using rigorous
analysis and consider three-dimensional effects.

@@

\begin{wrapfigure}[11]{r}{0.5\textwidth}
  \vspace{-8pt}
  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:amphiphilic_assembly} \footnotesize
  Self-organization under amphiphilic boundary condition. (a) Granules
  first match hydrophobic tails (red), (b) then align length-wise. (c)
  The same pattern of self-organization holds in three dimensions, as
  simulated by Kohl, Corona, and
  Veerapaneni~\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
In the double-well potential case, equation~\eqref{eqn:phase} is a
nonlinear Allen-Cahn equation. This situation models granules immersed
in a two-phase fluid (e.g., granules in an emulsion) where there is an
interesting interplay between the long-range alignment of granules and
the diffusive interface energy of the free boundary between fluid
phases. On unbounded domains like $\Omega(t)$, Allen-Cahn equations can
have multiple solutions~\cite{Alama1997StationaryLS,
Alikakos2008OnAE, Bronsard1993OnTB, Byeon2014SolutionsOH, Byeon2013OnAP,
Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF}.
To have one solution $\phi$ for each $t$, 
we must reformulate~\eqref{eqn:phase} as
the following initial value problem with transport:
\begin{align}
  \label{eqn:phase_transport}
  \phi_t + \uu \cdot \nabla
  = -\beta \frac{\delta E}{\delta \phi}
  = \beta(\epsilon^2 \Delta \phi - W'(\phi)),
  \quad \phi(\xx,0) = \phi_0(\xx),
\end{align}
for initial data $\phi_0$. The modified system enjoys an energy law
similar to~\eqref{eq:energy_law} with an additional dissipation term
involving the square the Euler-Lagrange derivative $\frac{\delta
E}{\delta \phi}$ and dampening factor $\beta > 0$. There are several
works dealing with the characterization of the geometric evolution of
interfaces under the Allen-Cahn and Cahn-Hilliard
equations~\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF,
Dai2019WeakSF, Promislow2017ExistenceBA, Dai2015CompetitiveGE,
Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
Dai2013GeometricEO, Promislow2022UndulatedBI, Gera2017CahnHilliardOS}
and well-posedness
results when coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
Liu2012StrongSF, Giorgini2019WellPosednessOA, Wu2022WellposednessOA,
Gal2010AsymptoticBO, Giorgini2020DiffuseIM, Giorgini2019UniquenessAR}.
The proposed research extends these results to problems with moving
domains. A closely related and strongly developing direction in the area
of nematics liquid crystals concerns the interaction of Landau-de Gennes
functionals with colloids, and studies the qualitative structure of
defects around single or multiple colloidal
particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
Alama2021SaturnRD, PhysRevE.96.042702}.

@@

The second problem considers the approximation of elastic energy of
curves and surfaces, and seeks to make rigorous the simulation results
of~\cite{FuQuRyYo22, Fu2018_SIAM}. We employ the so-called
``amphiphilic'' boundary condition that leads a collection of
granules to form bilayers. Referring to
Figure~\ref{fig:amphiphilic_assembly}, 
\begin{align}
\label{eq:amphiphilic_BC}
  \phi(\xx) = \tfrac{1}{2}\left(\dd_i \cdot 
    (\xx - \aa_i)/c_i + 1\right), \quad \xx \in \Gamma_i,
\end{align}
where $\dd_i$ is the unit length director, $\aa_i$ is the center, and
$c_i$ the ``radius'' of the $i$th granule. The phase $\phi$ takes values
close to $1$ in the direction $\dd_i$, representing a hydrophobic tail,
and values close to $0$ in the direction $\dd_i$ representing the
hydrophilic head.

@@

Sharp interface models represent a membrane vesicle as an
inextensible, continuous, closed surface $\Sigma$ with elastic energy
\begin{align}
  \label{eq:Canham-Helfrich}
  \int_{\Sigma} k_B(H - k_0)^2\, dS,
\end{align}
where $H$ is the mean curvature, $k_0$ is a spontaneous curvature, and
$k_B$ is a bending modulus. One can also account
for spatially dependent spontaneous curvature
\cite{PhysRevE.79.031926,Lowengrub13,mahapatra_saintillan_rangamani_2020}
and for extensibility by
including in~\eqref{eq:Canham-Helfrich} an additional stretching term
$k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are
the deformed and equilibrium area densities respectively
\cite{chabanon2017}.

@@

Finally, to consider three-dimensional effects, we will generalize
Problem 2 to \emph{numerically} study the energies of amphiphilic
granules confined to surfaces. Recent works on nematics on a surface have
studied the interplay between surface geometry and a director
field~\cite{Nestler2020PropertiesOS, Nitschke2018NematicLC,
Nestler2018OrientationalOO, Nitschke2019HydrodynamicII,
Nitschke2020LiquidCO}. Researchers have formulated finite element
methods~\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
Nestler2019AFE} and studied minimizers~\cite{Segatti2014EquilibriumCO,
Segatti2014AnalysisOA}. In biophysics, researchers
have derived the generalized Helfrich energy for lipid bilayers that
involves coupling effects between lipid tilt to director
splay~\cite{Hamm2000ElasticEO, Terzi2019CurvatureTiltTO, Terzi2019ACQ,
  Terzi2017NovelTC, Pinigin2020NewCT,Rangamani20140463}. It contains~\eqref{eq:Canham-Helfrich}
as a special case.
\begin{quotation}
  \noindent
  \textbf{Problem 3.} Simulate surfaces made up of three-dimensional,
  amphiphilic granules. Numerically investigate the limiting energy for
  large-$N_b$ suspensions.
\end{quotation}
We will study Problem 3 by simulating large granule-number membranes.
If, after thoroughly sampling shapes and boundary conditions,
it turns out that the granule energies are not described by
a nematic or  Helfrich-type energy, then we will change
hypotheses and look for alternative sharp interface elastic energies.
PI Ryham is well-qualified to lead this investigation.
In his much noticed Biophysical Journal and Nature
papers~\cite{RyKlYaCo16, Chetal16}, he calculated least energy
paths for \emph{membrane fusion} using a surface-director model based on
the general Helfrich energy. The energy barriers 
proved consistent with later results from molecular dynamic
simulation and experiment~\cite{SmRiMu19, 2017PNAS..114.1238F}.
